### 2021-06-21 paper.tex
couldn't resist; should sleep

Combined, the preceding arguments allows us to  see the chain of actions \begin{equation}
\text{extended} \stackrel{S}{\longleftrightarrow} 
\text{anomaly} \stackrel{T}{\longleftrightarrow} 
\text{anomaly} \stackrel{S}{\longleftrightarrow} 
\text{extended} \stackrel{T}{\longleftrightarrow} 
\begin{array}{c}
\text{extended}\\
\text{and with $\mathfrak{P}$} 
\end{array} 
\stackrel{S}{\longleftrightarrow} 
\begin{array}{c}
\text{extended }\\
\text{and with $\mathfrak{P}$} 
\end{array} 
\stackrel{T}{\longleftrightarrow} 
\label{nontrivial-chain}
\end{equation}
where `extended' stands for $\bZ_4$ without the background term $\frac12\mathfrak{P}(E)$,
`extended with $\mathfrak{P}$' is for $\bZ_4$ with the background term,
and `anomaly' is $\bZ_2\times \bZ_2$ with the anomaly \eqref{anom}.

\subsection{Anomalies from $\SL(2,\bZ_2)$ action} 
Comparing the chains of actions \eqref{trivial-chain} and \eqref{nontrivial-chain} we determined above 
and Table~\ref{table:2group},
we see that the anomaly is automatically determined and 
we obtain the result already presented in Table~\ref{table:main}.
There is a small puzzle to be resolved, but it's already 1pm. I am going to sleep...

>>>>

\def\ewith{
\begin{array}{c}
\text{extended}\\
\text{with $\mathfrak{P}$} 
\end{array} 
}
\def\ewithout{
\begin{array}{c}
\text{extended}\\
\text{without $\mathfrak{P}$} 
\end{array} 
}
Combined, the preceding arguments allows us to  see the chain of actions \begin{equation}
\ewith \stackrel{T}{\longleftrightarrow} 
\ewithout \stackrel{S}{\longleftrightarrow} 
\text{anomaly} \stackrel{T}{\longleftrightarrow} 
\text{anomaly} \stackrel{S}{\longleftrightarrow} 
\ewithout \stackrel{T}{\longleftrightarrow} 
\ewith \stackrel{S}{\longleftrightarrow} 
\label{nontrivial-chain}
\end{equation}
where `extended' stands for $\bZ_4$ without the background term $\frac12\mathfrak{P}(E)$,
`extended with $\mathfrak{P}$' is for $\bZ_4$ with the background term,
and `anomaly' is $\bZ_2\times \bZ_2$ with the anomaly \eqref{anom}.

\subsection{Anomalies from $\SL(2,\bZ_2)$ action} 
Comparing the chains of actions \eqref{trivial-chain} and \eqref{nontrivial-chain} we determined above 
and Table~\ref{table:2group},
we see that the anomaly is automatically determined and 
we obtain the result already presented in Table~\ref{table:main}.

More precisely, when `extended' or `anomaly' is involved, 
we should better distinguish $\Spin(2n_c)$ and $T\Spin$, etc.
We find the following:{\small \begin{equation}
\begin{array}{r@{\,}l|cccccc}
(n_c,&n_f)  & T\Spin & \Spin & \SO_+ & T\SO_+& T\SO_- & \SO_- \\
\hline
(\text{odd},&\text{even}) & \text{e.with} &\text{e.without} & \text{anom} & \text{anom} & \text{e.without } & \text{e.with} \\
(\text{even},&\text{odd}) & \text{anom} & \text{anom} & \text{e.without } & \text{e.with}  & \text{e.with} & \text{e.without} \\
(\text{odd},&\text{odd}) & \text{e.without } & \text{e.with} & \text{e.with} & \text{e.without}
 &  \text{anom} & \text{anom}   \end{array} 
\end{equation}}
